The \dealii{} Library, Version 9.3

### 2021-06-19 9.3/paper.tex
Write text about preCICE

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item preCICE: \todo[inline]{TODO}
\end{itemize}

>>>>

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
\item ``\texttt{Laplace equation coupled to an external simulation program}'' was
  contributed by David Schneider and Benjamin Uekermann at Technical University
  of Munich. It shows by extending \texttt{step-4}---a time-dependent Poisson
  problem~---how to surface-couple a \dealii application with a simple external 
  application, using the \texttt{preCICE} 
  library~\cite{bungartz2016precice, lindner2020exafsa}. \texttt{preCICE},
  however, also allows to couple \dealii to actual external simulation softwares, 
  such as OpenFOAM, SU2, CalculiX, or FEniCS, using provided adapter classes. 
  For more details visit their webpage
  \url{https://precice.org/} and check out the numerous \dealii tutorials there,
  showing, i.a., interesting fluid-structure interaction application cases.
\end{itemize}
